### 2007-01-12 Documentation/Paper2/paper2.tex
*** empty log message ***

(or: ``GLoBES 3.0 release: From user-defined systematics to the simulation of non-standard physics'')
\end{center}}
{\begin{center}
{\large\bf (General Long Baseline Experiment Simulator)}
\end{center}}
\renewcommand{\thefootnote}{\alph{footnote}}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=14cm]{GLOBES}
\end{center}
\caption{\label{fig:GLOBES} General concept of the \GLOBES\ package.}
\end{figure}

@@

\GLOBESN\ allows the modification of this Hamiltonian and the whole probability engine without
re-compilation of the \GLOBES\ software. This is implemented
by using pointers for the functions calling the standard probability engine, which can be changed if
a different probability engine is registered. For example, a user may just copy the standard probability
engine of \GLOBES , and modify it, and register it. An important prerequisite for the ability to handle
more than the standard six oscillation parameters (plus matter density) $\boldsymbol{\lambda}=(\theta_{12},\theta_{13}, \theta_{23}, \deltacp, \sdm, \ldm, \rho)$, \ie,
\begin{equation}
\boldsymbol{\lambda}=(\theta_{12},\theta_{13}, \theta_{23}, \deltacp, \sdm, \ldm, \rho, \eta_1, \hdots, \eta_n)
\end{equation}
with $n$ non-standard parameters $\eta_j$. These parameters can be accessed in the usual way, see \Ref~\cite{Manual}.
For example, non-standard Hamiltonian effects in the $e$-$\tau$-sector may be introduced by modifying \equ{ham} to
\begin{equation}
 \mathcal{\hat{H}} = \mathcal{H}(n_e) + 
\left(
\begin{array}{ccc}
0 & 0 & \epsilon_{e \tau} \\
0 & 0 & 0 \\
\epsilon_{e \tau}^* & 0 & 0 
\end{array}
\right)
\end{equation}
In this case, there are two more real parameters, such as the absolute value and phase of $\epsilon_{e \tau}$.
In the literature, the non-standard physics feature in \GLOBES\ as experimental feature has been used for damping effects (such as neutrino decoherence, decay, \etc) in \Ref~\cite{Blennow:2005yk}, Hamiltonian-level effects (such as non-standard matter effects) in \Ref~\cite{Blennow:2005qj}, and mass-varying neutrinos in \Ref~\cite{Schwetz:2005fy} by implementing an environment dependence of neutrino mass.  ANY OTHERS (PH!)?

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=9cm]{reactor}
\end{center}
\mycaption{\label{fig:reactor} Luminosity scaling of the $\stheta$ sensitivity for different systematical error assumptions (90\% confidence level). The thick curve corresponds to \equ{chi2reactor} for $\sigma_R=\sigma_{\mathrm{corr}}=2.8\%$, $\sigma_N=\sigma_F=\sigma_{\mathrm{uncorr}}=0.6\%$ and an additional calibration error. Figure similar to \Ref~\cite{Huber:2006vr}. MISLEADING: WHY IS THE LUMINOSITY
OF THE ``FAR DETECTOR'' ON THE X-AXIS? SHOULD THIS NOT BE THE SAME AS THE ONE FOR THE NEAR DETECTOR? 
AT LEAST IF I INTERPRET THE CODE CORRECTLY [WW]}
\end{figure}

>>>>

(Alternative: ``GLoBES 3.0: From the simulation of non-standard physics to user-defined systematics'')

(Alternative: ``GLoBES 3.0: Simulation of non-standard physics and multi-source multi-detector
setups'')

\end{center}}
{\begin{center}
{\large\bf (General Long Baseline Experiment Simulator)}
\end{center}}
\renewcommand{\thefootnote}{\alph{footnote}}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=14cm]{GLOBES}
\end{center}
\mycaption{\label{fig:GLOBES} General concept of the \GLOBES\ package.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{reactorNSI}
\end{center}
\mycaption{\label{fig:reactorNSI} Fit in the $\stheta$-$\sigma_E$-plane for the simulated values
$\stheta=\sigma_E=0$ (figure similar to \Ref~\cite{Blennow:2005yk}). Here $\sigma_E$ is an additional non-standard parameter describing the wave packet width of the neutrino oscillation wave packet. The figure is computed with
{\tt example6.c} coming with the \GLOBESN\ distribution (and higher).}
\end{figure}

\GLOBESN\ allows the modification of this Hamiltonian and the whole probability engine without
re-compilation of the \GLOBES\ software. This is implemented
by using pointers for the functions calling the standard probability engine, which can be changed if
a different probability engine is registered. For example, a user may just copy the standard probability
engine of \GLOBES , and modify it, and register it. An important prerequisite for the ability to handle
more than the standard six oscillation parameters (plus matter density) $\boldsymbol{\lambda}=(\theta_{12},\theta_{13}, \theta_{23}, \deltacp, \sdm, \ldm, \rho)$, \ie,
\begin{equation}
\boldsymbol{\lambda}=(\theta_{12},\theta_{13}, \theta_{23}, \deltacp, \sdm, \ldm, \rho, \eta_1, \hdots, \eta_n)
\end{equation}
with $n$ non-standard parameters $\eta_j$. These parameters can be accessed in the usual way, see \Ref~\cite{Manual}.
For example, non-standard Hamiltonian effects in the $e$-$\tau$-sector may be introduced by modifying \equ{ham} to
\begin{equation}
 \mathcal{\hat{H}} = \mathcal{H}(n_e) + 
\left(
\begin{array}{ccc}
0 & 0 & \epsilon_{e \tau} \\
0 & 0 & 0 \\
\epsilon_{e \tau}^* & 0 & 0 
\end{array}
\right)
\label{equ:nsi}
\end{equation}
In this case, there are two more real parameters, such as the absolute value and phase of $\epsilon_{e \tau}$.
In the literature, the non-standard physics feature in \GLOBES\ as experimental feature has been used for damping effects (such as neutrino decoherence, decay, \etc) in \Ref~\cite{Blennow:2005yk}, Hamiltonian-level effects (such as non-standard matter effects) in \Ref~\cite{Blennow:2005qj}, and mass-varying neutrinos in \Ref~\cite{Schwetz:2005fy} by implementing an environment dependence of neutrino mass.  ANY OTHERS (PH!)?
We show in \figu{reactorNSI} a result from \Ref~\cite{Blennow:2005yk} provided as {\tt example6.c} in the \GLOBES\
distribution. Compared to \equ{nsi}, the underlying physics takes place at the probability level, \ie, 
\equ{probs} (for details, see \Ref~\cite{Blennow:2005yk}). In {\tt example6.c}, an analytical implementation
of this physics is used for simplicity.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=9cm]{reactor}
\end{center}
\mycaption{\label{fig:reactor} Luminosity scaling of the $\stheta$ sensitivity for different systematical error assumptions (90\% confidence level, figure similar to \Ref~\cite{Huber:2006vr}). The thick curve corresponds to \equ{chi2reactor} for $\sigma_R=\sigma_{\mathrm{corr}}=2.8\%$, $\sigma_N=\sigma_F=\sigma_{\mathrm{uncorr}}=0.6\%$ and an additional calibration error. The figure is computed with {\tt example5.c} provided with the \GLOBES\ software.
 MISLEADING: WHY IS THE LUMINOSITY
OF THE ``FAR DETECTOR'' ON THE X-AXIS? SHOULD THIS NOT BE THE SAME AS THE ONE FOR THE NEAR DETECTOR? 
AT LEAST IF I INTERPRET THE CODE CORRECTLY [WW]}
\end{figure}
